The Five Pillars of Translational Digital Medicine

### 2022-04-30 main.tex
abstract

SH is supported by a Health Foundation Improvement Science Fellowship, and by funding from 
Biomedical Research Centre based at the University College Hospitals (UCLH) National Health Service (NHS) Foundation Trust and University College London (UCL). NS is supported by funding from Health Data Research UK. SH, TK, and NS are supported funds from the National Institute for Health Research (Artificial Intelligence, Digitally adapted, hyper-local real-time bed forecasting to manage flow for NHS wards, AI AWARD01786) and NHS-X. The views expressed in this publication are those of the author(s) and not necessarily those of the National Institute for Health Research, NHS-X or the Department of Health and Social Care. WL is supported by a UKRI Ernest Rutherford Fellowship.

>>>>

SH is supported by a Health Foundation Improvement Science Fellowship, and by funding from  the Biomedical Research Centre based at the University College Hospitals (UCLH) National Health Service (NHS) Foundation Trust and University College London (UCL). NS is supported by funding from Health Data Research UK. SH, TK, and NS are supported funds from the National Institute for Health Research (Artificial Intelligence, Digitally adapted, hyper-local real-time bed forecasting to manage flow for NHS wards, AI AWARD01786) and NHS-X.  WL is supported by a UKRI Ernest Rutherford Fellowship.
The views expressed in this publication are those of the author(s) and not necessarily those of the National Institute for Health Research, NHS-X or the Department of Health and Social Care.
